### 2019-08-09 reports/thesis/chapters/5_inference.tex
Tidy up figures in inference

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}

@@

To summarise the proposed method, Figure \ref{fig:inference_flowchart} shows a flowchart which summarises the process of the experiment and defect detection and how the empirical null filter fits in. The CAD model was used as a blueprint for the manufacture of the test sample. Projections of the test sample and the simulated projection were obtained and compared under the face of uncertainty. The uncertainty was modelled using the replicated projections. The test statistics from the comparison were filtered using the empirical null filter and converted to $p$-values. A threshold was used for the $p$-values to classify pixels as positive for defects or not.

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{../figures/flowchart.eps}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
  \label{fig:inference_flowchart}
\end{figure}

@@

For good results, the faces of the test sample were segmented. This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly. Manual segmentation was easy to do because a cuboid has 6 faces. However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.

While the empirical null filter performed well ABS test sample, it failed in the titanium test sample due to dominate effects on the edges. This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection. This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point it cannot perform and fails.

>>>>

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.45cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}

@@

To summarise the proposed method, Figure \ref{fig:inference_flowchart} shows a flowchart of the process of the experiment and defect detection and how the empirical null filter fits in. The CAD model was used as a blueprint for the manufacture of the test sample. Projections of the test sample and the simulated projection were obtained and compared under the face of uncertainty. The uncertainty was modelled using the replicated projections. The test statistics from the comparison were filtered using the empirical null filter and converted to $p$-values. A threshold was used for the $p$-values to classify pixels as positive for defects or not.

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{../figures/flowchart.pdf}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
  \label{fig:inference_flowchart}
\end{figure}

@@

For good results, the faces of the test sample were segmented. This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly. Manual segmentation was easy to do because a cuboid has 6 faces. However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces. Automatic segmentation may be possible with geometrical information from the CAD model.

While the empirical null filter performed well for the ABS test sample, it failed in the titanium test sample due to dominating effects on the edges. This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection. This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecification null statistics cannot be distinguished from non-null statistics.
